Effects of CHILDREN's programs

### 2020-02-25 paper.Rnw
comments in factor analysis
fghj
moved examples in Rnw file upwards
deleted superfluous stuff

@@

@@

@@

Equation\\

\begin{equation}
\label{ModelProdu}
\ln y_{it} = \beta_0 + \beta_k \ln k_{it-1}^{n} + \beta_n \ln n_{it} + \beta_m \ln m_{it} + \beta_t D_t + \beta_i D_i + \epsilon_{it}
\end{equation}

@@

          float.env = "sidewaystable")
# row.names(tableDispSumm) <- c("$Disp_t^n$", "$Disp_t^d$", "$Disp_t^a$", "$Y_t^n$", "$Y_t^d$", "$GDP_t$")
# colnames(tableDispSumm) <- c("$Corr(X_t, X_{t-1})$", "$\\sigma(X)$", "$\\frac{\\sigma(X)}{\\sigma(Y)}$", "$\\frac{\\sigma(X)}{\\sigma(GDP)}$")
# tableDispSumm <- xtable(tableDispSumm, caption = "Productivity dispersion: Summary statistics", digits = 3, align = "crccc")
# print(tableDispSumm, sanitize.text.function = function(x) {x}, caption.placement = "top")
@

@@

% table1_selfworth <- stargazer(lm1_selfworth,
%                     lm2_selfworth,
%                     lm3_selfworth,
%                     lm4_selfworth,
%           title = "Regression Results",
%           order = c('Constant', 'treatEF'),
%           omit = c('id104','id105','id106','id108','id109','id111','id112','id113','id114','id118','id122',
%                    'id123','id124','id125','id130','id131','id132','id133','id136','id137','id139','id141',
%                    'id142','id165','id186','id187','id188','id189','id190','id191','id192','id193','id194',
%                    'id209','id213','id214','id215','id216','id217','id218','id219','id220','id221','id226',
%                    'id233','id249','id255','id269','id270','id281','id282','id403','id404','id417','id418',
%                    'id437','id482','id483','id599','id600','id601','id602','id623','id684','id685','id686',
%                    'id687','dummy_2012','dummy_2013','dummy_2014','dummy_2015','dummy_2016','dummy_2017',
%                    'dummy_2018', 'id'
%                   ),
%           add.lines = list(c("ID fixed effects", 'No', 'No', 'Yes', 'Yes'),
%                            c('Time fixed effects', 'No', 'Yes', 'No', 'Yes')),
%           align = TRUE)

% \begin{table}[!htbp] \centering 
%   \caption{Regression Results} 
%   \label{} 
% \begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
% \\[-1.8ex]\hline 
% \hline \\[-1.8ex] 
%  & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
% \cline{2-5} 
% \\[-1.8ex] & \multicolumn{4}{c}{selfworth} \\ 
% \\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
% \hline \\[-1.8ex] 
%  Constant & 2.796^{***} & 2.870^{***} & 2.774^{***} & 2.847^{***} \\ 
%   & (0.065) & (0.095) & (0.092) & (0.107) \\ 
%   & & & & \\ 
%  treatEF & 0.249^{***} & 0.320^{***} & 0.253^{***} & 0.333^{***} \\ 
%   & (0.074) & (0.097) & (0.075) & (0.100) \\ 
%   & & & & \\ 
% \hline \\[-1.8ex] 
% ID fixed effects & No & No & Yes & Yes \\ 
% Time fixed effects & No & Yes & No & Yes \\ 
% Observations & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} \\ 
% R$^{2}$ & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.036} \\ 
% Adjusted R$^{2}$ & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.017} & \multicolumn{1}{c}{0.022} & \multicolumn{1}{c}{0.015} \\ 
% Residual Std. Error & \multicolumn{1}{c}{0.642 (df = 428)} & \multicolumn{1}{c}{0.644 (df = 421)} & \multicolumn{1}{c}{0.642 (df = 427)} & \multicolumn{1}{c}{0.645 (df = 420)} \\ 
% F Statistic & \multicolumn{1}{c}{11.417$^{***}$ (df = 1; 428)} & \multicolumn{1}{c}{1.916$^{*}$ (df = 8; 421)} & \multicolumn{1}{c}{5.752$^{***}$ (df = 2; 427)} & \multicolumn{1}{c}{1.724$^{*}$ (df = 9; 420)} \\ 
% \hline 
% \hline \\[-1.8ex] 
% \textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
% \end{tabular} 
% \end{table}

>>>>

% models with robust standard errors texreg
% https://github.com/DeclareDesign/estimatr/issues/316

@@

Equation with\\

\begin{equation}
\label{ModelProdu}
\ln y_{it}^{n} = \beta_0 + \beta_k \ln k_{it-1}^{n} + \beta_n \ln n_{it} + \beta_m \ln m_{it} + \beta_t D_t + \beta_i D_i + \epsilon_{it}
\end{equation}

Regression fit ouput with texreg

@@

<<Health Regressions time plots, echo=FALSE, results='asis', message=FALSE>>=
Health_timeplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Health_Year.Rds")
print(Health_timeplots)
@

@@

@@

          float.env = "sidewaystable")
@

@@
